Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-06-06 paper.tex
Update Homogeneous Equilibrium test

We integrate Eqns.~\ref{eqn:num_x}-\ref{eqn:num_tau} with adaptive step sizes,
using the 5th-order Dormand-Prince algorithm \cite{pres2007-nr_3rd_ed}.
After a step is taken, the error is estimated for each variable.
If the maximum of these errors exceeds some absolute or relative threshold
the step size is decreased and the step recomputed,
if it is below some threshold the next step size is increased.
% see OdeIntegrators::AdaptiveDense
% and OdeSteppers::DormandPrince5
% and OdeControllers::ProportionalIntegral_Base::StepSizeToAttempt
% and OdeErrorMeasures::ScaledAbsRel
\todo{specify}

@@

\subsection{Homogeneous Equilibrium}
\label{ssec:test_equilibrium}
Homogeneous matter, optically thick. Plot in Fig.~\ref{fig:homogeneous_isotropic}.
\todo{describe test}

\subsection{Doppler Shift}
\label{ssec:test_doppler}
Homogeneous matter moving with v in +z direction. Stationary observer.
Plot in Fig.~\ref{fig:avg_eps_doppler}.
\todo{describe test}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-homogeneous_isotropic}
  \caption{Equilibrium distribution functions in a homogeneous background at
    $\varrho=6.22 \times 10^{12}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=5$~MeV,
    $Y_e=0.3$,
    using the LS220 equation of state, in which the equilibrium
    neutrino chemical potentials are
    $\mu_{\nu_e}=-\mu_{\bar{\nu}_e}=62.04$~MeV, and 
    $\mu_{\nu_x}=0$.
    The solid lines give the analytic Fermi-Dirac distribution,
    and the points are computed via ray tracing.
    Described in Sec.~\ref{ssec:test_equilibrium}}
  \label{fig:homogeneous_isotropic}
\end{figure}

>>>>

We integrate Eqns.~\ref{eqn:num_x}--\ref{eqn:num_tau} with adaptive step sizes,
using the 5th-order Dormand-Prince algorithm \cite{pres2007-nr_3rd_ed}.
After a step is taken, the error is estimated for each variable.
If the maximum of these errors exceeds some absolute or relative threshold
the step size is decreased and the step recomputed,
if it is below some threshold the next step size is increased.
% see OdeIntegrators::AdaptiveDense
% and OdeSteppers::DormandPrince5
% and OdeControllers::ProportionalIntegral_Base::StepSizeToAttempt
% and OdeErrorMeasures::ScaledAbsRel
\todo{specify}

@@

To test our algorithm, we integrate the ray tracing equations
(Eqns.~\ref{eqn:num_x}--\ref{eqn:num_tau}) in the following configurations,
and compare $f$ or moments of $f$ to known analytic solutions, or in some
cases to fiducial numerical calculations.

\subsection{Homogeneous Equilibrium}
\label{ssec:test_equilibrium}
In an optically thick region the radiation field is in thermodynamic equilibrium
with the matter.
We set up a large slab of matter in two homogeneous configurations
representative of the fluid in the Massive Collapsed Star test
(Sec.~\ref{ssec:test_collapse}) at two different radii:
at 50~km
For comparision with Collapsed Star test, we use the LS180 equation of state,
in which the equilibrium
neutrino chemical potentials are
$\mu_{\nu_e}=-0.639$~MeV, and 
$\mu_{\nu_e}=5.771$~MeV respectively
($\mu_{\bar{\nu}_e}=-\mu_{\nu_e}$ and $\mu_{\nu_x}=0$).
Plot in Fig.~\ref{fig:homogeneous_isotropic}.
\todo{run test at this thermodynamic point}

\subsection{Doppler Shift}
\label{ssec:test_doppler}
We reproduce the test above, but with the matter moving in
in the $+z$ direction, with the observer stationary.
Plot in Fig.~\ref{fig:avg_eps_doppler}.
\todo{describe test}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-homogeneous_equilibrium}
  \caption{Equilibrium distribution functions in a homogeneous background
    at two thermodynamic points,
    representative of the collapse profile at
    50~km ($\varrho=1.235 \times 10^{11}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=4$~MeV,
    $Y_e=0.12$) and
    200~km ($\varrho=3.026\times 10^{7}\,{\rm g}\,{\rm cm}^{-3}$,
    $T=0.5$~MeV,
    $Y_e=0.5$).
    Described in Sec.~\ref{ssec:test_equilibrium}}
  \label{fig:homogeneous_isotropic}
\end{figure}
